Efficient Planning for Sokoban with Answer Set Programming - A Case Study

### 2018-08-20 BATexFiles/Draft.tex
again a few lines changed in the tex

%Sokoban is a logistics game, where the player controls a character in a warehouse. The goal of the game is to move all crates in the warehouse on one of the target fields. The rules state that crates cannot be stacked on one field and crates cannot be pushed if there is a crate or a wall blocking the way. Each player move is a step into one of the four directions in a two-dimensional grid. If the player would collide with a crate, the crate is pushed into the direction of the player-movement. A level is usually satisfied when each crate is pushed on a target; also we can conclude that each target would be covered with a crate, because the amount of targets and crates is equal.
\section{State of the Art}
Gordon Wilfong published 1991 that all motion planning problems with moving obstacles are NP-hard \cite{WilfongNPhard} by reducing 3Sat to such a problem. He didnt answer the question whether Sokoban is also PSPACE-complete. That was answered by Joseph C Culberson \cite{PSpaceComplete} in 1997. He showed that it is possible to emulate a linear bounded automaton by constructing a level. The solution to this constructed level, if there is any, will have a length in $\Theta (|w|+t(|w|))$, where $w$ is the input and $t(|w|)$ is the amount of transitions the LBA made. This shows PSPACE-completeness

>>>>

%Sokoban is a logistics game, where the player controls a character in a warehouse. The goal of the game is to move all crates in the warehouse on one of the target fields. The rules state that crates cannot be stacked on one field and crates cannot be pushed if there is a crate or a wall blocking the way. Each player move is a step into one of the four directions in a two-dimensional grid. If the player would collide with a crate, the crate is pushed into the direction of the player-movement. A level is usually satisfied when each crate is pushed on a target; also we can conclude that each target would be covered with a crate, because the amount of targets and crates is equal.
\section{State of the Art}
\textbf{Complexity:} Gordon Wilfong published in 1991 that all motion planning problems with moving obstacles are NP-hard \cite{WilfongNPhard}. He proved this by reducing $3$-$Sat$ to such a problem. The question whether Sokoban is PSPACE-complete remained open until 1997, when Joseph C. Culberson published his paper "Sokoban is PSPACE-complete" \cite{PSpaceComplete}. He found a transformation algorithm to transform an LBA into a level of Sokoban, with the solution to the level having a number of steps in $\Theta (|w|+t(|w|))$, where $w$ is the input and $t(|w|)$ is the amount of transitions the LBA made. %This shows PSPACE-hardness and Sokoban is known to be in PSPACE, so Sokoban is PSPACE-complete.
\newline%He didnt answer the question whether Sokoban is also PSPACE-complete. That was answered by Joseph C Culberson \cite{PSpaceComplete} in 1997. He showed that it is possible to emulate a linear bounded automaton by constructing a level. The solution to this constructed level, if there is any, will have a length in $\Theta (|w|+t(|w|))$, where $w$ is the input and $t(|w|)$ is the amount of transitions the LBA made. This shows PSPACE-completeness
\textbf{Approaches:} There are loads of different researches regarding approaches to Sokoban. I decided which to show. Botea et al. found out that heuristics, while significantly improving chess AI, do not seem to help for planning the soko puzzle \cite{BoteaHeuristicsVsPlanning}. Planning would be a better approach. So to get there and create good plans like humans would, the solver will start meta-reasoning by recognizing rooms and tunnels. Then using those rooms and tunnels to create a plan where first a way is found to bring the crates from the room where theyre at to the target room. Then another plan is made to organize crates in a room.
\newline
\textbf{Macromoves:} Macromoves are a planning strategy that is so successful it is implemented in several good Sokoban solvers. The best example would be Rolling Stone, an excellent Sokoban solver, with a lot of optimizations implemented. One of the optimizations is the possibility to create macromoves for tunnels to reduce all states in the tunnel to one or two, reducing the search space severely.
\newline
\textbf{Deadlock Detection:} 
%What is a Deadlock, with picture. Why do you detect those? How do you detect those? Better when you know the level or know basic deadlocks to look for. In the halls without tunnels it should be less hard
\textbf{Relevance Cutting:}
\newline
\textbf{Lexicographical Ordering:}
\newline
